DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-02 paper/overview.tex
Change track image
Added new image, track_new2.png
..

\begin{table}[h]
  \centering
  \begin{tabular}{|l|l|}
    \hline
    Item                    & cost (\$) \\
    \hline
    Raspberry Pi 3 Model B  & 35 \\
    New Bright 1:24 scale RC car       & 10 \\
    Playstation Eye camera  &  7 \\
    Pololu DRV8835 motor hat&  8 \\
    External battery pack   & 10 \\
    \hline
    Total                   & 70 \\
    \hline
  \end{tabular}
  \caption{DeepPicar's bill of materials (BOM)}
  \label{tbl:carbom}
\end{table}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth, angle=270]{figs/track_new}
  \caption{A track for training/testing.\fixme{replace this}}
  \label{fig:track}
\end{figure}

>>>>

\begin{table}[h]
  \centering
  \begin{tabular}{|r|r|}
    \hline
    Item                    & cost (\$) \\
    \hline
    Raspberry Pi 3 Model B  & 35 \\
    New Bright 1:24 scale RC car       & 10 \\
    Playstation Eye camera  &  7 \\
    Pololu DRV8835 motor hat&  8 \\
    External battery pack \& misc.   & 10 \\
    \hline
    Total                   & 70 \\
    \hline
  \end{tabular}
  \caption{DeepPicar's bill of materials (BOM)}
  \label{tbl:carbom}
\end{table}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth]{figs/track_new2}
  \caption{A track for training/testing.\fixme{replace this}}
  \label{fig:track}
\end{figure}
